---
title: "Pursuit Study: Long Term Influence of Hypertension Medication on Health Benefits"
author: "Amelia Johnson, Brian Kundinger, Emily Friedman"
output: pdf_document
---

import data
```{r}
library(readxl)
library(survival)
library(ggplot2)
PURSUIT <- read_excel("PURSUIT.xls")
```

reformat variables
```{r}
PURSUIT$DEATH180 <- as.numeric(PURSUIT$DEATH180)
PURSUIT$DTHMI180 <- as.numeric(PURSUIT$DTHMI180)
PURSUIT$DTHMI30 <- as.numeric(PURSUIT$DTHMI30)
PURSUIT$HXPTCA <- as.numeric(PURSUIT$HXPTCA)
PURSUIT$ENROLLMI <- as.numeric(PURSUIT$ENROLLMI)
PURSUIT$STDEP <- as.numeric(PURSUIT$STDEP)
PURSUIT$USPT <- as.numeric(PURSUIT$USPT)
PURSUIT$INTERV72 <- as.numeric(PURSUIT$INTERV72)
PURSUIT$CBLKPRH <- as.numeric(PURSUIT$CBLKPRH)
PURSUIT$DIGPRH <- as.numeric(PURSUIT$DIGPRH)
PURSUIT$NTRIVPR <- as.numeric(PURSUIT$NTRIVPR)
PURSUIT$BBLKPR <- as.numeric(PURSUIT$BBLKPR)
PURSUIT$HTN <- as.numeric(PURSUIT$HTN)
PURSUIT$HXDIAB <- as.numeric(PURSUIT$HXDIAB)
PURSUIT$LIPIDS <- as.numeric(PURSUIT$LIPIDS)
PURSUIT$FAMHX <- as.numeric(PURSUIT$FAMHX)
PURSUIT$PREVMI <- as.numeric(PURSUIT$PREVMI)
PURSUIT$HXCHF <- as.numeric(PURSUIT$HXCHF)
PURSUIT$HXCABG <- as.numeric(PURSUIT$HXCABG)
PURSUIT$HXRINSUF <- as.numeric(PURSUIT$HXRINSUF)
PURSUIT$PVD <- as.numeric(PURSUIT$PVD)
PURSUIT$RACE <- as.factor(PURSUIT$RACE)
PURSUIT$SMOKSTAT <- as.factor(PURSUIT$SMOKSTAT)
PURSUIT$RALES <- as.factor(PURSUIT$RALES)
PURSUIT$MALE <- as.numeric(PURSUIT$MALE)
PURSUIT$PULSEB <- as.numeric(PURSUIT$PULSEB)
PURSUIT$SOURCE <- as.factor(PURSUIT$SOURCE)
PURSUIT$TX <- gsub("High", replacement=1, PURSUIT$TX)
PURSUIT$TX <- gsub("Placebo", replacement=0, PURSUIT$TX)
PURSUIT$TX <- as.numeric(PURSUIT$TX)
PURSUIT$PULSEB <- as.numeric(PURSUIT$PULSEB)
PURSUIT$DTHMIDAY <- as.numeric(PURSUIT$DTHMIDAY)
PURSUIT$HEIGHT <- as.numeric(PURSUIT$HEIGHT)
PURSUIT$BMI <- as.numeric(PURSUIT$BMI)
PURSUIT$CREATCL <- as.numeric(PURSUIT$CREATCL)
PURSUIT$MAXCKRAT <- as.numeric(PURSUIT$MAXCKRAT)
PURSUIT$MAXMBRAT <- as.numeric(PURSUIT$MAXMBRAT)
PURSUIT$BASCKRAT <- as.numeric(PURSUIT$BASCKRAT)
PURSUIT$BASMBRAT <- as.numeric(PURSUIT$BASMBRAT)
PURSUIT$SXTOTX <- as.numeric(PURSUIT$SXTOTX)
```

```{r}
ggplot(data= PURSUIT, aes(x=TX, fill=DTHMI30)) +
         geom_bar()
```


QUESTION 1: What baseline characteristics are associated with time from symptoms to 
  treatment in the population of ACS patients studied in PURSUIT?
  
Plan: linear model selection and univariate and multiple analysis for each variable

QUESTION 2: PURSUIT was an international trial, so it is natural to wonder
  whether time from symptoms to treatment is different in different
  in different regions of the world.  In particular, is the time between
  symptoms and treatment in the US different from that for patients in 
  the rest of the world?

Plan: ANOVA, confidence interval graph

QUESTION 3: Controlling for other relevant baseline factors, are the frequencies
  of 30-day and 180-day outcomes (death/MI) associated with time from
  symptoms to treatment?

Plan:
a) Attempt: logistic regression on DTHMI30 and DTHMI 180
  Results: TX is significant for 30 day but not 180
          SXTOTX is initially significant but in the opposite direction than hypothesized
          it is not significant for either 30 or 180 when controlling for the patient's conditions

make baseline sub dfs          
```{r}
baselinePursuit30wTX <- select(PURSUIT, DTHMI30, HXPTCA, ENROLLMI, STDEP, USPT, CBLKPRH, DIGPRH,NTRIVPR,BBLKPR,HTN,HXDIAB,LIPIDS,FAMHX,PREVMI,HXCHF,HXCABG,HXRINSUF,PVD,HXPAIN,RACE,SMOKSTAT,PULSEB,AGE,WEIGHT,HEIGHT,SYSBP,DIABP,BMI,CREATCL, RALES, MALE,SOURCE,BASCKRAT,BASMBRAT, TX, SXTOTX)

baselinePursuit30wo <- select(PURSUIT, DTHMI30, HXPTCA, ENROLLMI, STDEP, USPT, CBLKPRH, DIGPRH,NTRIVPR,BBLKPR,HTN,HXDIAB,LIPIDS,FAMHX,PREVMI,HXCHF,HXCABG,HXRINSUF,PVD,HXPAIN,RACE,SMOKSTAT,PULSEB,AGE,WEIGHT,HEIGHT,SYSBP,DIABP,BMI,CREATCL, RALES, MALE,SOURCE,BASCKRAT,BASMBRAT,SXTOTX)

baselinePursuit180wTX <- select(PURSUIT, DTHMI180, HXPTCA, ENROLLMI, STDEP, USPT, CBLKPRH, DIGPRH,NTRIVPR,BBLKPR,HTN,HXDIAB,LIPIDS,FAMHX,PREVMI,HXCHF,HXCABG,HXRINSUF,PVD,HXPAIN,RACE,SMOKSTAT,PULSEB,AGE,WEIGHT,HEIGHT,SYSBP,DIABP,BMI,CREATCL, RALES, MALE,SOURCE,BASCKRAT,BASMBRAT, TX, SXTOTX)

baselinePursuit180wo <- select(PURSUIT, DTHMI180, HXPTCA, ENROLLMI, STDEP, USPT, CBLKPRH, DIGPRH,NTRIVPR,BBLKPR,HTN,HXDIAB,LIPIDS,FAMHX,PREVMI,HXCHF,HXCABG,HXRINSUF,PVD,HXPAIN,RACE,SMOKSTAT,PULSEB,AGE,WEIGHT,HEIGHT,SYSBP,DIABP,BMI,CREATCL, RALES, MALE,SOURCE,BASCKRAT,BASMBRAT, SXTOTX)
```

logistic regression for 30 days: TX significance with controls, SXTOTX is not
```{r}
summary(glm(data=PURSUIT, DTHMI30 ~ SXTOTX, family = binomial(link=logit)))

summary(glm(data=PURSUIT, DTHMI30 ~ TX, family = binomial(link=logit)))

summary(glm(data=PURSUIT, DTHMI30 ~ SXTOTX+TX, family = binomial(link=logit)))

summary(glm(data=baselinePursuit30wTX, DTHMI30 ~ SXTOTX*TX, family = binomial(link=logit)))

#without treatment 
summary(glm(data=baselinePursuit30wo, DTHMI30 ~ ., family = binomial(link=logit)))

#including treatment
summary(glm(data=baselinePursuit30wTX, DTHMI30 ~ ., family = binomial(link=logit)))

#summary(glm(data=baselinePursuit30, DTHMI30 ~ .+TX*SXTOTX, family = binomial(link=logit)))
```

logistic regression for 180 days: TX almost significant for death mi 180
```{r}
summary(glm(data=PURSUIT, DTHMI180 ~ SXTOTX, family = binomial(link=logit)))

summary(glm(data=PURSUIT, DTHMI180 ~ TX, family = binomial(link=logit)))

summary(glm(data=PURSUIT, DTHMI180 ~ SXTOTX+TX, family = binomial(link=logit)))

summary(data=PURSUIT, DTHMI180 ~ SXTOTX*TX, family = binomial(link=logit))

#without treatment 
summary(glm(data=baselinePursuit180wo, DTHMI180 ~ ., family = binomial(link=logit)))

#including treatment
summary(glm(data=baselinePursuit180wTX, DTHMI180 ~ ., family = binomial(link=logit)))

#summary(glm(data=baselinePursuit180, DTHMI180~ .+TX*SXTOTX, family = binomial(link=logit)))
```

b) Survival Analysis with cox PH model for DTHMI DAY
  Results: Cox PH also shows that SXTOTX is not significant in Predicting DTHMIDAY ingeneral, before 30days or after 30 days, including when adjusting for baseline characteristics
  
death and death mi without controls: TX, time both not significant
time almost significant for death mi
```{r}
baselineTemp<- select(PURSUIT, DTHMIDAY, HXPTCA, ENROLLMI, STDEP, USPT, CBLKPRH, DIGPRH,NTRIVPR,BBLKPR,HTN,HXDIAB,LIPIDS,FAMHX,PREVMI,HXCHF,HXCABG,HXRINSUF,PVD,HXPAIN,RACE,SMOKSTAT,PULSEB,AGE,WEIGHT,HEIGHT,SYSBP,DIABP,BMI,CREATCL, RALES, MALE,SOURCE,BASCKRAT,BASMBRAT, TX, SXTOTX)

res.cox <- coxph(Surv(DTHMIDAY)~TX, data =baselineTemp)
summary(res.cox)
res.cox <- coxph(Surv(DTHMIDAY)~., data =baselineTemp)
summary(res.cox)

baselineb430 <- baselineTemp %>% filter(DTHMIDAY <=30)
baselineb4180<- baselineTemp %>% filter(DTHMIDAY <=180)

res.cox <- coxph(Surv(DTHMIDAY)~TX, data =baselineb430)
summary(res.cox)
res.cox <- coxph(Surv(DTHMIDAY)~., data =baselineb430)
summary(res.cox)

res.cox <- coxph(Surv(DTHMIDAY)~TX, data =baselineb4180)
summary(res.cox)
res.cox <- coxph(Surv(DTHMIDAY)~., data =baselineb4180)
summary(res.cox)
```

death and death mi before and after 30 days without controls: 
TX, time both not significant without controlling
```{r}
before30 <- PURSUIT %>% filter(DTHMI30==1)
after30 <- PURSUIT %>% filter(DTHMI30==0)
```
before:no significance 
```{r}
res.cox <- coxph(Surv(DEATHDY)~TX, data =before30)
res.cox
summary(res.cox)

res.cox <- coxph(Surv(DEATHDY) ~ TX + SXTOTX, data =before30)
res.cox
summary(res.cox)

res.cox <- coxph(Surv(DTHMIDAY)~TX, data =before30)
res.cox
summary(res.cox)

res.cox <- coxph(Surv(DTHMIDAY) ~ TX + SXTOTX, data =before30)
res.cox
summary(res.cox)
```
after:no significance
```{r}
res.cox <- coxph(Surv(DEATHDY)~TX, data =after30)
res.cox
summary(res.cox)

res.cox <- coxph(Surv(DEATHDY) ~ TX + SXTOTX, data =after30)
res.cox
summary(res.cox)

res.cox <- coxph(Surv(DTHMIDAY)~TX, data =after30)
res.cox
summary(res.cox)

res.cox <- coxph(Surv(DTHMIDAY) ~ TX + SXTOTX, data =after30)
res.cox
summary(res.cox)
```


control for baseline variables:

create baseline dfs
```{r}
baselinePursuitdth <- select(PURSUIT, DEATHDY, DTHMI30, HXPTCA, ENROLLMI, STDEP, USPT, CBLKPRH, DIGPRH,NTRIVPR,BBLKPR,HTN,HXDIAB,LIPIDS,FAMHX,PREVMI,HXCHF,HXCABG,HXRINSUF,PVD,HXPAIN,RACE,SMOKSTAT,PULSEB,AGE,WEIGHT,HEIGHT,SYSBP,DIABP,BMI,CREATCL, RALES, MALE,SOURCE,BASCKRAT,BASMBRAT, TX, SXTOTX)

baselinePursuitdmi <- select(PURSUIT, DTHMIDAY, DTHMI30, HXPTCA, ENROLLMI, STDEP, USPT, CBLKPRH, DIGPRH,NTRIVPR,BBLKPR,HTN,HXDIAB,LIPIDS,FAMHX,PREVMI,HXCHF,HXCABG,HXRINSUF,PVD,HXPAIN,RACE,SMOKSTAT,PULSEB,AGE,WEIGHT,HEIGHT,SYSBP,DIABP,BMI,CREATCL, RALES, MALE,SOURCE,BASCKRAT,BASMBRAT, TX, SXTOTX)
```
death and death mi with controls: no significance
```{r}
res.cox <- coxph(Surv(DEATHDY)~., data =baselinePursuitdth)
summary(res.cox)

res.cox <- coxph(Surv(DTHMIDAY)~., data =baselinePursuitdmi)
summary(res.cox)

```

death and death mi before and after 30 with controls:
```{r}
before30dth <- baselinePursuitdth %>% filter(DTHMI30==1)
after30dth <- baselinePursuitdth %>% filter(DTHMI30==0)
before30dmi <- baselinePursuitdmi %>% filter(DTHMI30==1)
after30dmi <- baselinePursuitdmi %>% filter(DTHMI30==0)
```
time is almost significant for death before 30 days
```{r}
res.cox <- coxph(Surv(DEATHDY)~., data =before30dth)
summary(res.cox)

res.cox <- coxph(Surv(DEATHDY) ~., data =after30dth)
summary(res.cox)

res.cox <- coxph(Surv(DTHMIDAY)~., data =before30dmi)
summary(res.cox)

res.cox <- coxph(Surv(DTHMIDAY) ~ ., data =after30dmi)
summary(res.cox)
```


c) Kaplin-Meyer exploration of DTHMI and DEATH days

death mi
```{r}
surv_obj <- Surv(time=PURSUIT$DTHMIDAY)
kmcurve <- survfit(surv_obj ~ PURSUIT$TX, data=PURSUIT)
library(survminer)
ggsurvplot(kmcurve, data=PURSUIT, pval=T) + 
 
  ggtitle("Death or MI Survival Rates for Treatment vs. Placebo")

```

death
```{r}
surv_obj <- Surv(time=PURSUIT$DEATHDY)
kmcurve <- survfit(surv_obj ~ PURSUIT$TX, data=PURSUIT)
ggsurvplot(kmcurve, data=PURSUIT, pval=T) + 
  ggtitle("Death Survival Rates for Treatment vs. Placebo")
```

death mi at 30 and 180: TX significant at the 30 day mark
```{r}
surv_obj <- Surv(time=PURSUIT$DTHMIDAY, event= PURSUIT$DTHMI180)
kmcurve <- survfit(surv_obj ~ PURSUIT$TX, data=PURSUIT)
ggsurvplot(kmcurve, data=PURSUIT, pval=T)

surv_obj <- Surv(time=PURSUIT$DTHMIDAY, event= PURSUIT$DTHMI30)
kmcurve <- survfit(surv_obj ~ PURSUIT$TX, data=PURSUIT)
ggsurvplot(kmcurve, data=PURSUIT, pval=T)
```
death  at 30 and 180 days: no significance, TX is not significant in preventing death at all 
```{r}
surv_obj <- Surv(time=PURSUIT$DEATHDY, event= PURSUIT$DTHMI180)
kmcurve <- survfit(surv_obj ~ PURSUIT$TX, data=PURSUIT)
ggsurvplot(kmcurve, data=PURSUIT, pval=T)

surv_obj <- Surv(time=PURSUIT$DEATHDY, event= PURSUIT$DTHMI30)
kmcurve <- survfit(surv_obj ~ PURSUIT$TX, data=PURSUIT)
ggsurvplot(kmcurve, data=PURSUIT, pval=T)
```
Results: TX is significant before 30 days but not at 180 days for DTHMIDAY
        TX seems like it is only significant in preventing heart attacks, not death

Explore difference between the death  and death mi groups 
```{r}
table(PURSUIT$DTHMI180)
table(PURSUIT$DTHMI30)
table(PURSUIT$DEATH180)
#table(betterP$SurvDHTMIDAY)
```

Hypothesis: TX is only significant in preveting mi, not death
Test with Logistic Regression:

create new variable for whether or not DTHMIDY was a death or an mi
```{r}
#did they survive the dthmiday
require(dplyr)
table(PURSUIT$TX)
betterP <- PURSUIT %>%
  mutate(SurvDTHMIDAY=(DEATHDY > DTHMIDAY)) %>%
mutate(SurvDTHMIDAY=as.numeric(SurvDTHMIDAY))
betterP$SurvDTHMIDAY

```
only include the people who got integrilin
```{r}
head(betterP)
table(betterP$TX)
length(betterP$SurvDTHMIDAY )
table(betterP$SurvDTHMIDAY)
betterP30 <- betterP %>% filter(DTHMIDAY<=30)

length(betterP30$SurvDTHMIDAY)
table(betterP30$TX)
table(betterP30$SurvDTHMIDAY)
betterP30$SurvDTHMIDAY <- gsub("1", replacement="Survived", betterP30$SurvDTHMIDAY)
betterP30$SurvDTHMIDAY <- gsub("0", replacement="Died", betterP30$SurvDTHMIDAY)
betterP30$TX <- gsub("1", replacement="High", betterP30$TX)
betterP30$TX <- gsub("0", replacement="Placebo", betterP30$TX)
betterP30$SurvDTHMIDAY
table(betterP30$SurvDTHMIDAY,as.factor(betterP30$TX))
table(betterP30$SurvDTHMIDAY,as.factor(betterP30$INTERV72))

#betterP <- betterP %>% (DEATH30 = ifelse(betterP$DEATHDY == 31, 0,1))

#betterP <- betterP %>% (MIONLYDAY = ifelse(betterP$SurvDTHMIDAY==1,betterP$DTHMIDAY, NA))
```


create new data frames
```{r}
baselinePursuit30 <- select(betterP, DTHMI30, HXPTCA, ENROLLMI, STDEP, USPT, CBLKPRH, DIGPRH,NTRIVPR,BBLKPR,HTN,HXDIAB,LIPIDS,FAMHX,PREVMI,HXCHF,HXCABG,HXRINSUF,PVD,HXPAIN,RACE,SMOKSTAT,PULSEB,AGE,WEIGHT,HEIGHT,SYSBP,DIABP,BMI,CREATCL, RALES, MALE,SOURCE,BASCKRAT,BASMBRAT,SXTOTX, SurvDTHMIDAY, TX)

#this removes nas
#mi only before 30
mionly30<- baselinePursuit30 %>% filter(SurvDTHMIDAY==1)

#death before 30
dthonly30<- baselinePursuit30 %>% filter(SurvDTHMIDAY==0)

baselinePursuit180 <- select(betterP, DTHMI180, HXPTCA, ENROLLMI, STDEP, USPT, CBLKPRH, DIGPRH,NTRIVPR,BBLKPR,HTN,HXDIAB,LIPIDS,FAMHX,PREVMI,HXCHF,HXCABG,HXRINSUF,PVD,HXPAIN,RACE,SMOKSTAT,PULSEB,AGE,WEIGHT,HEIGHT,SYSBP,DIABP,BMI,CREATCL, RALES, MALE,SOURCE,BASCKRAT,BASMBRAT, SXTOTX, SurvDTHMIDAY,TX)

#mi only before 180
mionly180<- baselinePursuit180 %>% filter(SurvDTHMIDAY==1)

#death before 180
dthonly180<- baselinePursuit180 %>% filter(SurvDTHMIDAY==0)
```

logistic regression for 30 days: TX significance with controls, SXTOTX is not
```{r}
#30
summary(glm(data=mionly30, DTHMI30 ~ TX, family = binomial(link=logit)))
#ns
summary(glm(data=mionly30, DTHMI30 ~ ., family = binomial(link=logit)))
#0.1
summary(glm(data=dthonly30, DTHMI30 ~ TX, family = binomial(link=logit)))
#0.1
summary(glm(data=dthonly30, DTHMI30 ~ ., family = binomial(link=logit)))
#0.05

#180
summary(glm(data=dthonly180, DTHMI180 ~ TX, family = binomial(link=logit)))
#ns
summary(glm(data=dthonly180, DTHMI180 ~ ., family = binomial(link=logit)))
#0.05
summary(glm(data=dthonly180, DTHMI180 ~ TX, family = binomial(link=logit)))
#ns
summary(glm(data=dthonly180, DTHMI180 ~ ., family = binomial(link=logit)))
#0.05
```
logistic regression for 25 days
```{r}
#only before 25 days
pursuit25 <- PURSUIT%>%
    mutate(DTHMI25 = ifelse (DTHMIDAY <= 24, 1, 0))
```
```{r}
summary(glm(data=pursuit25, DTHMI25 ~ TX, family = binomial(link=logit)))

baselineTemp <- select(pursuit25, DTHMI25, HXPTCA, ENROLLMI, STDEP, USPT, CBLKPRH, DIGPRH,NTRIVPR,BBLKPR,HTN,HXDIAB,LIPIDS,FAMHX,PREVMI,HXCHF,HXCABG,HXRINSUF,PVD,HXPAIN,RACE,SMOKSTAT,PULSEB,AGE,WEIGHT,HEIGHT,SYSBP,DIABP,BMI,CREATCL, RALES, MALE,SOURCE,BASCKRAT,BASMBRAT, SXTOTX,TX)

summary(glm(data=baselineTemp, DTHMI25 ~ ., family = binomial(link=logit)))
```

Give up on this rabbit hole

QUESTION 5:

```{r}
pursuit.timecluster <- betterP %>% 
  mutate(SXTOTXcat = cut(PURSUIT$SXTOTX, breaks = c(0,0.05,8,16,24,200))) 

require(survival)
surv_object <- Surv(time = pursuit.timecluster$DTHMIDAY)
KMcurve <- survfit(surv_object ~ SXTOTXcat, data = pursuit.timecluster)
require(ggplot2)
require(survminer)
survplot0 <- ggsurvplot(KMcurve, data = pursuit.timecluster, pval = TRUE) +
    ggtitle("Probability of Death or MI before and after 24 hour SXTOTX") 

survplot0$title <- survplot0$plot +theme(plot.title = element_text(hjust = 0.5))
survplot0$title

# Does this work to show the effects at 30 days?
surv_object <- Surv(time = pursuit.timecluster$DTHMIDAY, event = pursuit.timecluster$DTHMI30)

KMcurve <- survfit(surv_object ~ SXTOTXcat, data = pursuit.timecluster)
ggsurvplot(KMcurve, data = pursuit.timecluster, pval = TRUE, xlim = c(0,30), ylim = c(.5, 1))

```

baseline df
```{r}
baselinetemp <- select(pursuit.timecluster, DTHMIDAY, HXPTCA, ENROLLMI, STDEP, USPT, CBLKPRH, DIGPRH,NTRIVPR,BBLKPR,HTN,HXDIAB,LIPIDS,FAMHX,PREVMI,HXCHF,HXCABG,HXRINSUF,PVD,HXPAIN,RACE,SMOKSTAT,PULSEB,AGE,WEIGHT,HEIGHT,SYSBP,DIABP,BMI,CREATCL, RALES, MALE,SOURCE,BASCKRAT,BASMBRAT, SXTOTXcat, SurvDTHMIDAY, TX)
```

cox model for time to treatment cohorts
```{r}
res.cox <- coxph(Surv(DTHMIDAY)~SXTOTXcat, data = baselinetemp)
summary(res.cox)
res.cox <- coxph(Surv(DTHMIDAY)~., data = baselinetemp)
summary(res.cox)
```


logistic regression for time to treatment cohorts
```{r}
baselinetemp <- select(pursuit.timecluster, DTHMI30, HXPTCA, ENROLLMI, STDEP, USPT, CBLKPRH, DIGPRH,NTRIVPR,BBLKPR,HTN,HXDIAB,LIPIDS,FAMHX,PREVMI,HXCHF,HXCABG,HXRINSUF,PVD,HXPAIN,RACE,SMOKSTAT,PULSEB,AGE,WEIGHT,HEIGHT,SYSBP,DIABP,BMI,CREATCL, RALES, MALE,SOURCE,BASCKRAT,BASMBRAT, SXTOTXcat, TX)
```
```{r}
summary(glm(data=baselinetemp, DTHMI30 ~ SXTOTXcat, family = binomial(link=logit)))
```

